Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions

### 2017-01-12 writing/phase_transition/phase_transition.tex
Phase transition 85% done

@@

We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched on the Fig. \ref{pic:potential_sym_asym}; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
% 
\begin{figure}[ht]
\center{\includegraphics[width=0.65\linewidth]{pic/potential_sym_asym.png}}
\caption{
Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
\label{pic:potential_sym_asym}
}
\end{figure}
%
The Hamiltonian for the system of weakly interacting exciton polaritons in an external $U(x)$ can be written in the second quantized form as:
%
\begin{equation}
\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
\label{eq:gpe_hamiltonian}
\end{equation}
%
where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ is two-body (polariton-polariton) scattering length.
In the paper we use so-called two-mode representation of $\hat{\psi}$ supposing
%
\begin{equation}
\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
\label{eq:two_modes}
\end{equation}
%
where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
It's instructive to recast $\Phi_{1,2}(x)$ as
%
\begin{equation}
\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
\label{eq:basic_modes}
\end{equation}
%
where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real wavefunctions obeying stationary Gross-Pitaevskii equations, respectively
%
\begin{equation}
\mu_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
\label{eq:stationary}
\end{equation}
%
and normalization condition $\int \Phi_{\pm}^2 dx = 1$.
Here $\mu_{\pm}$ are chemical potentials.
As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit ``hat'' design for simplicity).
Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
% 
\begin{equation}
\begin{array}{lcl}
\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
\end{array}
\label{eq:hamiltonian}
\end{equation}
%
where we made some denotations
%
\begin{equation}
\begin{array}{c}
\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\
\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\
C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\
G = \mu_- - \mu_+ - 2\Gamma.
\end{array}
\label{eq:subs}
\end{equation}
%

Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double well potential.
It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate
%
\begin{equation}
G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2).
\label{eq:tunneling_rate}
\end{equation}
%
The contribution from relevant coefficients on can be estimated from variational ansatz
%
\begin{equation}
\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]
\label{eq:two_modes_eq}
\end{equation}
%
where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of intra-well distance $x_0$ is shown.
It is important that at differences between them rapidly vanishes with increasing of distance $x_0$.
We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{Raghavan} and cf. }.
%
\begin{figure}[ht]
\center{\includegraphics[width=0.65\linewidth]{pic/ypm_x0.png}}
\caption{Dependence of $\gamma_{ij} / g$ versus $x_0 / a$ \label{pic:gamma_pm_vs_g}}
\end{figure}
%

@@

To elucidate important quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
% 
\begin{subequations}
\begin{align}
\hat{S}_x = \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos(\phi) - \sin(\phi) \dfrac{d}{d \phi}, \\
\quad \hat{S}_y = \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin(\phi) + \cos(\phi) \dfrac{d}{d \phi}, \\
\hat{S}_z = \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
\end{align}
\label{eq:pseudo_spin}
\end{subequations}
%
where $s = \dfrac{N}{2} >> 1$ is large {\red $C$ - number}, $\phi$ is phase variable.
The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations
%
\begin{equation}
[S_x, S_y] = iS_z, \quad[S_z, S_x] = iS_y, \quad[S_y, S_z] = iS_x.
\label{eq:commutation_relations}
\end{equation}
%
After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
%
\begin{equation}
\begin{array}{lcl}
H & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta(s-\dfrac{1}{2})\sin{2\phi} - B\sin{\phi}) \dfrac{d}{d \phi} \\
&& - Bs \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
\end{array}
\label{eq:hamiltinian_s}
\end{equation}
%
where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig. \ref{pic:gamma_pm_vs_g}

Hamiltonian (\ref{eq:hamiltinian_s}) corresponds to Schrodinger equation
%
\begin{equation}
\begin{array}{l}
(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta(s - \dfrac{1}{2})\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
+ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
\end{array}
\label{eq:schrodinger}
\end{equation}
%
where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{Anglin}.
Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
%
\begin{equation}
\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
\end{equation}
%
where
%
\begin{equation}
\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
\end{equation}
%
is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
It is possible to eliminate the term with first derivative in Eq.(\ref{eq:schrodinger}) applying the transformation
%
\begin{equation}
\Phi(\phi) = \Psi(z) \exp \Big( s \log \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
\label{eq:transformation_of_phi}
\end{equation}
%
where
%
\begin{equation}
z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \sqrt{\lambda})
\end{equation}
is new phase variable; $F(\phi, \sqrt{\lambda})$ is incomplete elliptic integral of the first kind.
In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.

@@

Here we suppose that {\red $\Lambda < 1$}.
This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
In general all terms in (\ref{eq:potential}) should be kept.
The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
If $2\lambda < \Lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
{\red equation for small oscillations}

In the other limit, for $2 \lambda > \Lambda$, two minima of $V_0(z)$ with coordinates
%
\begin{equation}
\cn{z_{min}} = \frac{\Lambda (2 \lambda - 1)}{0.5 \Lambda^2 - 2 \lambda (1 - \lambda)}
\label{eq:z_minima}
\end{equation}
%
appears both for Josephson and Fock regimes, cf. Fig. \ref{phase_potential}b,c.  
The depth of the potential minima depends on the $\lambda$ parameter.
It is interesting to note that for {\red $\lambda > \dots$} potential $V_0(z)$ presumes local minimum at \dots

@@

@@

>>>>

\author{D. A. Dolinina}
\email{dasha.doly@gmail.com}
\affiliation{ITMO University, St. Petersburg 197101, Russia}

@@

We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched on the Fig. \ref{pic:potential_sym_asym}; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
% 
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
\caption{
Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
\label{pic:potential_sym_asym}
}
\end{figure}
%
The Hamiltonian for the system of weakly interacting exciton polaritons in an external $U(x)$ can be written in the second quantized form as:
%
\begin{equation}
\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
\label{eq:gpe_hamiltonian}
\end{equation}
%
where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ is two-body (polariton-polariton) scattering length.
In the paper we use so-called two-mode representation of $\hat{\psi}$ supposing
%
\begin{equation}
\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
\label{eq:two_modes}
\end{equation}
%
where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
It's instructive to recast $\Phi_{1,2}(x)$ as
%
\begin{equation}
\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
\label{eq:basic_modes}
\end{equation}
%
where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real wavefunctions obeying stationary Gross-Pitaevskii equations, respectively
%
\begin{equation}
\mu_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
\label{eq:stationary}
\end{equation}
%
and normalization condition $\int \Phi_{\pm}^2 dx = 1$.
Here $\mu_{\pm}$ are chemical potentials.
As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit ``hat'' design for simplicity).
Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
% 
\begin{equation}
\begin{array}{lcl}
\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
\end{array}
\label{eq:hamiltonian}
\end{equation}
%
where we made some denotations
%
\begin{equation}
\begin{array}{l}
\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\
A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}); \quad \Gamma = \frac{1}{2} (\gamma_{++} - \gamma_{--}); \\
C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-}); \quad G = \mu_- - \mu_+ - 2\Gamma.
\end{array}
\label{eq:subs}
\end{equation}
%

Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double well potential.
It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate
%
\begin{equation}
G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2).
\label{eq:tunneling_rate}
\end{equation}
%
The contribution from relevant coefficients on can be estimated from variational ansatz
%
\begin{equation}
\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]
\label{eq:two_modes_eq}
\end{equation}
%
where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of intra-well distance $x_0$ is shown.
It is important that at differences between them rapidly vanishes with increasing of distance $x_0$.
We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{Raghavan} and cf. }.
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.png}}
\caption{Dependence of $\gamma_{ij} / g$ versus $x_0 / a$ \label{pic:gamma_pm_vs_g}}
\end{figure}
%

@@

To elucidate important quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
% 
\begin{subequations}
\begin{align}
\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos{\phi} - \sin{\phi} \dfrac{d}{d \phi}, \\
\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
\end{align}
\label{eq:pseudo_spin}
\end{subequations}
%
where $s = \dfrac{N}{2} >> 1$ is large {\red $C$ - number}, $\phi$ is phase variable.
The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations
%
\begin{equation}
[S_x, S_y] = iS_z, \quad[S_z, S_x] = iS_y, \quad[S_y, S_z] = iS_x.
\label{eq:commutation_relations}
\end{equation}
%
After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
%
\begin{equation}
\begin{array}{lcl}
H & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta(s-\dfrac{1}{2})\sin{2\phi} - B\sin{\phi}) \dfrac{d}{d \phi} \\
&& - Bs \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
\end{array}
\label{eq:hamiltinian_s}
\end{equation}
%
where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig. \ref{pic:gamma_pm_vs_g}

Hamiltonian (\ref{eq:hamiltinian_s}) corresponds to Schrodinger equation
%
\begin{equation}
\begin{array}{l}
(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta(s - \dfrac{1}{2})\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
+ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
\end{array}
\label{eq:schrodinger}
\end{equation}
%
where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{Anglin}.
Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
%
\begin{equation}
\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
\end{equation}
%
where
%
\begin{equation}
\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
\end{equation}
%
is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
It is possible to eliminate the term with first derivative in Eq.(\ref{eq:schrodinger}) applying the transformation
%
\begin{equation}
\Phi(\phi) = \Psi(z) \exp \Big( s \log \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
\label{eq:transformation_of_phi}
\end{equation}
%
where
%
\begin{equation}
z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)
\end{equation}
is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.

@@

Here we suppose that {\red $\Lambda < 1$}.
This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
In general all terms in (\ref{eq:potential}) should be kept.
The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
If $\Lambda < 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
{\red equation for small oscillations}

In the other limit, for $2 \lambda > \Lambda$, two minima of $V_0(z)$ with coordinates
%
\begin{equation}
\cn{z_{min}} = \frac{\Lambda (2 \lambda - 1)}{0.5 \Lambda^2 - 2 \lambda (1 - \lambda)}
\label{eq:z_minima}
\end{equation}
%
appears both for Josephson and Fock regimes, cf. Fig. \ref{phase_potential}b,c.  
The depth of the potential minima depends on the $\lambda$ parameter.
It is interesting to note that for {\red $\Lambda > 1 + 2\lambda + \sqrt{1 + 8\lambda}$} potential $V_0(z)$ presumes local minimum at {\red $\pm 2 K(\lambda)$}.

@@

Here we describe our approach to study the order of the phase transition and its temperature.
According to works of Owerre, Chudnovsky, Garanin et al. order of these transition can be determined from the period of oscillation $\tau(E)$ near the bottom of the potential.
Monotonically increasing $\tau(E)$ gives a second-order transition while nonmonotonic behaviour of $\tau(E)$ give a first-order transition.

We determiine the temperature of the transition like Owerre does.
At very low temperature, transition occur by quantum tunneling through the barrieer and the rate is governed by $\Gamma \sim e^{-B}$, where $B$ is the instanton action.
At high temperature the particle has the possibility of hopping over the barrier, in this case the rate is governed by $\Gamma \sim e^{-\Delta V / T}$, where $\Delta V$ is the energy barrier.
At a critical point these two transition rate are equal, there exist a crossover (first-order transition) temperature $T_{I}$ from quantum to a thermal regime, it's estimated as $T_{I} = \Delta V / B$.

The crossover temperature in the case of second-order transition can be estimated as $T_{II} = \omega_0 / 2 \pi$, where $\omega_0$ is a oscillation frequency of the thermon near the top of the barrier.

First, let's find out the dependence of the order on the parameters $\lambda$, $\Lambda$.
Expand the potential $V_0(z)$ into a Taylor series:
%
\begin{equation}
\begin{array}{lcl}
V_0(z) & = & \left( \frac{1}{4}\Lambda^2 - \lambda (1 - \lambda) \right) \left( z^2 + \frac{2\lambda - 1}{3} z^4 + o(z^4) \right) \\ && - \Lambda \left( 1 + \frac{2\lambda - 1}{2} z^2 + \frac{16\lambda^2 - 16\lambda + 1}{24} z^4 + o(z^4) \right) \\
& = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
\end{array}
\label{eq:potential_teylor}
\end{equation}
%
Classical equation of motion for the thermon reads as
%
\begin{equation}
\ddot{z} = s^2 \frac{d V_0}{dz}.
\label{eq:thermon}
\end{equation}
%
Equation for the small ocsillation near the top of the barrier:
%
\begin{equation}
\ddot{z} - s^2 \left( \tfrac{1}{2} \Lambda^2 - (2\lambda - 1) \Lambda - 2 \lambda (1 - \lambda) \right) z = 0.
\label{eq:thermon_small}
\end{equation}
%
It follows from (\ref{eq:thermon_small}) that, as mentioned above, when $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.

It's possible to show (for ex. using Poincare-Lindstedt method), that local behaviour of $\tau(E)$ is determined by the sign of the 4th degree in expansion (\ref{eq:potential_teylor}).
If potential has the form $-x^2 - x^4$ than $\tau(E)$ increase near the critical value $E_0$ (where the thermon vanish) and the 1st order phase transition take place.
In other case, if potential has the form $-x^2 + x^4$ than $\tau(E)$ decrease near the $E_0$ and the 2nd order phase transition occurs.
So, the border between 1st and 2nd phase transition is determined by the equaiton
%
\begin{equation}
\frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} = 0.
\end{equation}
%
Taking in account the barrier existence condition, and conditions on $\lambda$, $\Lambda$ parameters one can derive the analytic expression of the border
%
\begin{equation}
\Lambda = \frac{1 - 16\lambda + 16\lambda^2 + \sqrt{1 + 32\lambda - 32\lambda^2}}{4(2\lambda - 1)}.
\label{eq:order_border}
\end{equation}
%
We summarize our results on a picture below.
%
\begin{figure}[ht]
\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
\caption{Phase transition diagram}
\end{figure}
%

Consider the imaginary-time action
%
\begin{equation}
S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
\label{eq:thermon_action_1}
\end{equation}
%
Periodic, with $\tau_p = \hbar / k_B T$, solutions of (\ref{eq:thermon}) satisfy the relation
%
\begin{equation}
\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
\label{eq:total_energy}
\end{equation}
%
where $\tau_p$ is a thermon period corresponding to the energy level $E(\tau_p)$;
%
\begin{equation}
\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
\label{eq:thermon_period}
\end{equation}
%
here $z_{1,2}(E)$ -- turning points.
Using (\ref{eq:total_energy}) rewrite (\ref{eq:thermon_action_1}) in a form 
%
\begin{equation}
S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
\label{eq:thermon_action_2}
\end{equation}
%
We draw dependence $S(T)$ and $\tau_p(E)$ for the cases of the 1st and 2nd order phase transition.
For the sake of convenience we suppose that $V_0(z) = 0$ at minima surrounding the barrier.
So, $E = 0$ corrensponds to the separatrices instanton solution (May be we should make corresponding transformation earlier).
%
\begin{figure}[ht]
\center{\includegraphics[width=\linewidth]{pic/action_period_1st_order_transition.eps}}
\caption{1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$}
\end{figure}
%
\begin{figure}[ht]
\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition.eps}}
\caption{2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
\end{figure}
%

Now let's compute the temperature of the phase transition.
It follows from (\ref{eq:thermon_small}) that the frequency of small thermon oscillation near the top of the barrier can be computted as follows
%
\begin{equation}
\omega_0 = s \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
\label{eq:period_small}
\end{equation}
%
The temperature of the 2nd-order transition can be estimated as
\begin{equation}
T_{II} = (s  / 2 \pi) \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
\end{equation}

@@

\pagebreak
